Developmental trajectories of word recognition: a priming study in bilinguals

### 2023-11-20 manuscript/manuscript.qmd
Merge

```{r setup}
#| label: setup
#| echo: false
#| message: false
#| warning: false
# load objects
targets::tar_config_set(store = here::here("_targets"),
						script = here::here("_targets.R"))

@@

targets::tar_load(
	c(participants,
	  stimuli,
	  vocabulary,
	  attrition_trials,
	  attrition_participants,
	  bvq_data,
	  gaze,
	  data_bcn,
	  data_oxf
	))

targets::tar_load(
	c(model_fits_bcn,
	  model_loos_bcn,
	  model_fits_oxf,
	  model_loos_oxf
	))

# prepare data
attrition <- lst(participants,
				 attrition_participants,
				 attrition_trials) |>
	reduce(inner_join, by = join_by(session_id)) |>
	unnest_wider(matches("all"), names_sep = "_") |> 
	rename_with(\(x) gsub("is_valid_gaze_all_|is_valid_vocab_all", "", x))

@@

# set ggplot theme and colour palette
my_theme <- theme_minimal() +
	theme(panel.grid = element_blank(),
		  axis.line = element_line(colour = "black"),
		  text = element_text(size = 12, colour = "black"),
		  axis.text = element_text(colour = "black"))

@@

options(ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
		ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
		ggplot2.discrete.fill = clrs[c(1, 4, 5)],
		ggplot2.discrete.colour = clrs[c(1, 4, 5)],
		ggplot2.continuous.fill = ggplot2::scale_color_gradient,
		ggplot2.continuous.colour = ggplot2::scale_color_gradient)

@@

```{r}
#| label: participants-numbers-oxf
participants_oxf <- filter(participants, location=="Oxford")

@@

ages <- participants_oxf |> 
	summarise(n = n(),
			  n_participants = n_distinct(child_id),
			  across(age, lst(mean, sd, min, max)),
			  across(matches("doe_"), lst(mean, sd)),
			  age_vctr = list(age),
			  .by = c(lp, test_language))

suppressWarnings({
	time_diffs <- participants_oxf |>
		arrange(child_id, session_id, age) |>
		mutate(n_session = 1:n()) |>
		select(child_id, session_id, session_n, age) |> 
		filter(child_id %in% participants_oxf$child_id[duplicated(participants_oxf$child_id)]) |>
		pivot_wider(id_cols = child_id, 
					names_from = session_n, 
					values_from = age, 
					names_repair = janitor::make_clean_names) |> 
		rowwise() |>
		mutate(diff_min = x2-x1) |> 
		ungroup() |> 
		summarise(diff_min = min(diff_min, na.rm = TRUE))
})

@@

```{r vocab-values-oxf}
vocabulary_oxf <- inner_join(vocabulary, 
							 select(participants_oxf, session_id),
							 by = join_by(session_id))
```

@@

```{r fig-vocabulary-oxf}
#| label: fig-vocabulary-oxf
#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores from the recurrent participants are shown linked."
#| fig-width: 4
#| fig-height: 2.5
vocabulary_oxf |> 
	inner_join(filter(attrition_participants, is_valid_participant),
			   by = join_by(session_id)) |> 
	inner_join(select(participants, child_id, session_id, age_group),
			   by = join_by(child_id, session_id)) |> 
	ggplot(aes(age_group, l1_prop)) +
	geom_line(aes(group = child_id),
			  colour = "grey",
			  alpha = 1/4, linewidth = 3/4) +
	geom_dots(dotsize = 2,
			  colour = clrs[5],
			  fill = clrs[5],
			  scale = 1,
			  side = "both",
			  alpha = 3/4) +
	stat_summary(fun.data = mean_se,
				 geom = "errorbar",
				 linewidth = 1/2,
				 width = 0.1,
				 colour = "black",
				 show.legend = FALSE) +
	stat_summary(fun = mean,
				 geom = "point",
				 size = 1.5,
				 colour = "black",
				 show.legend = FALSE) +
	# geom_point(alpha = 1) +
	labs(x = "Age (months)",
		 y = "Vocabulary size",
		 colour = "Group",
		 fill = "Group") +
	scale_y_continuous(labels = scales::percent,
					   limits = c(0, 1)) +
	theme(panel.grid.major.y = element_line(linetype = "dotted",
											colour = "grey"),
		  legend.position = "top",
		  legend.title = element_blank())
```

```{r tbl-participants}
#| label: tbl-participants
#| tbl-cap: "Demographic and linguistic profile of testing sessions."
participants_bcn |> 
	unnest_wider(doe) |> 
	select(-matches("others")) |> 
	arrange(lp, test_language) |> 
	distinct(session_id, child_id, .keep_all = TRUE) |> 
	summarise(n = n(),
			  n_participants = length(unique(child_id)),
			  across(age, lst(mean, sd, min, max)),
			  across(matches("doe_"), lst(mean, sd)),
			  # age_vctr = list(age),
			  .by = c(lp, test_language)) |> 
	gt(rowname_col = "test_language",
	   groupname_col = "lp") |> 
	summary_rows(groups = c("Monolingual", "Bilingual"),
				 columns = matches("age"),
				 fns = list(Total ~ mean(.)),
				 fmt = ~ fmt_number(., decimals = 1, use_seps = FALSE)) |> 
	summary_rows(groups = c("Monolingual", "Bilingual"),
				 columns = c(n, n_participants),
				 fns = list(Total ~ sum(.)),
				 fmt = ~ fmt_integer(.)) |> 
	summary_rows(groups = c("Monolingual", "Bilingual"),
				 columns = matches("doe"),
				 fns = list(Total ~ mean(.)),
				 fmt = ~ fmt_number(., decimals = 1, scale_by = 100)) |> 
	grand_summary_rows(columns = matches("age"),
					   fns = list(Total ~ mean(.)),
					   fmt = ~ fmt_number(., decimals = 1)) |> 
	grand_summary_rows(columns = matches("doe"),
					   fns = list(Total ~ mean(.)),
					   fmt = ~ fmt_number(., decimals = 1, scale_by = 100)) |> 
	grand_summary_rows(columns = c(n, n_participants),
					   fns = list(Total ~ sum(.)),
					   fmt = ~ fmt_integer(.)) |> 
	# gt_plt_dist(age_vctr, type = "histogram") |>
	fmt_number(is.numeric, decimals = 1) |> 
	fmt_integer(c(n, n_participants)) |> 
	fmt_number(matches("doe"), decimals = 1, scale_by = 100) |> 
	cols_merge(c(age_min, age_max), 
			   pattern = "{1}-{2}") |> 
	cols_merge(c(age_mean, age_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(doe_catalan_mean, doe_catalan_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(doe_english_mean, doe_english_sd),
			   pattern = "{1} ({2})") |> 
	cols_merge(c(doe_spanish_mean, doe_spanish_sd), 
			   pattern = "{1} ({2})") |> 
	tab_spanner("Age (months)", matches("age")) |> 
	tab_spanner("Catalan", matches("catalan")) |> 
	tab_spanner("English", matches("english")) |> 
	tab_spanner("Spanish", matches("spanish")) |> 
	tab_spanner("Degree of Exposure (%)", matches("doe")) |> 
	cols_label(n = "Sessions",
			   n_participants = "Participants",
			   age_mean = "M (SD)",
			   age_min = "Range",
			   doe_catalan_mean = "M (SD)",
			   doe_english_mean = "M (SD)",
			   doe_spanish_mean = "M (SD)") |> 
	tab_style(cell_text(style = "italic"),
			  cells_column_labels()) |> 
	tab_style(cell_text(style = "italic"),
			  cells_column_spanners())
```

```{r vocab-values}
vocabulary_bcn <- vocabulary |> 
	inner_join(select(participants_bcn, session_id, lp, age_group),
			   by = join_by(session_id))

vocab_means <- vocabulary_bcn |> 
	summarise(across(c(total_prop, l1_prop), lst(mean, sd)),
			  n = n(),
			  .by = c(age_group, lp)) %>%
	mutate(across(matches("prop"), scales::percent)) %>%
	split(paste0("age_", gsub(" months", "", .$age_group))) |> 
	map(\(x) split(x, tolower(x$lp)))

n_imputed <- table(vocabulary_bcn$is_imputed)[2]
prop_imputed <- scales::percent(n_imputed/nrow(vocabulary_bcn))
n_pool <- nrow(bvq_data$vocabulary)
```

@@

```{r fig-vocabulary}
#| label: fig-vocabulary
#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages). Grey lines connect vocabulary size scores from the recurrent participants. For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested. Only participants included in the final data set are shown."
#| fig-width: 6
#| fig-height: 3.5
vocabulary_bcn |> 
	inner_join(filter(attrition_participants, is_valid_participant),
			   by = join_by(session_id)) |> 
	pivot_longer(c(total_prop, l1_prop),
				 names_to = "measure",
				 values_to = "prop",
				 names_transform = \(x) gsub("_prop", "", x)) |> 
	mutate(measure = if_else(measure=="l1", 
							 "L1 vocabulary", 
							 "Total vocabulary"),
		   is_imputed = if_else(is_imputed, "Imputed", "Observed") |> 
		   	factor(levels = c("Observed", "Imputed"))) |> 
	ggplot(aes(age_group, prop,
			   colour = lp,
			   fill = lp)) +
	facet_wrap(~measure) +
	geom_line(aes(group = child_id),
			  colour = "grey",
			  alpha = 1/4, linewidth = 3/4) +
	geom_dots(aes(side = if_else(lp=="Monolingual", "left", "right")),
			  dotsize = 2,
			  stroke = 1/2,
			  scale = 0.5,
			  alpha = 3/4) +
	stat_summary(fun.data = mean_se,
				 geom = "errorbar",
				 linewidth = 1/2,
				 width = 0.15,
				 colour = "black",
				 show.legend = FALSE,
				 position = position_dodge(width = 1.15)) +
	stat_summary(fun = mean,
				 geom = "point",
				 size = 1.5,
				 colour = "black",
				 show.legend = FALSE,
				 position = position_dodge(width = 1.15)) +
	# geom_point(alpha = 1) +
	labs(x = "Age (months)",
		 y = "Vocabulary size",
		 colour = "Group",
		 fill = "Group") +
	scale_y_continuous(labels = scales::percent,
					   limits = c(0, 1)) +
	theme(panel.grid.major.y = element_line(linetype = "dotted",
											colour = "grey"),
		  legend.position = "top",
		  legend.title = element_blank())
```

@@

```{r dataset_oxf}
attrition_oxf <- filter(attrition, location=="Oxford")
n_trials <- nrow(attrition_oxf)
n_sessions <- n_distinct(attrition_oxf$session_id)
n_participants <- n_distinct(attrition_oxf$child_id)
n_trials_valid <- nrow(filter(attrition_oxf,
							  is_valid_participant,
							  is_valid_trial))
n_sessions_valid <- attrition_oxf |> 
	distinct(child_id, .keep_all = TRUE) |> 
	pull(is_valid_participant) |> 
	sum()

n_participants_valid <- n_distinct(
	attrition_oxf[attrition_oxf$is_valid_participant, ]$child_id)

@@

n_longitudinal <- attrition_oxf |>
	filter(is_valid_participant,
		   is_valid_trial) |>
	distinct(child_id, session_n) |> 
	count(child_id, name = "times") |> 
	count(times)

@@

```{r coefs-oxf}
var_labels <- c("b_Intercept" = "Intercept",
				"b_age_std" = "Age (+1 SD)",
				"b_condition1" = "Condition (U vs. RN)",
				"b_condition2" = "Condition (RN vs. RC)")

model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_1,
									   data_bcn,
									   vars_dict = var_labels,
									   rope_interval = rope_interval)

coefs <- model_summary |> 
	mutate(.value = sprintf("%.3f", .value),
		   .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
		   .rope = scales::percent(.rope, accuracy = 0.01)) |> 
	split(janitor::make_clean_names(model_summary$.variable))
```

@@

tbl_data <- model_summary |>
	select(.variable_name, .value, .lower, .upper, .rope, .type) |>
	mutate(.variable_name = gsub("×", "$\\\\times$", .variable_name),
		   .hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
		   .rope = case_when(is.na(.rope) ~ "-",
		   				  .rope > 0.9999 ~ "1",
		   				  .rope < 0.00001 ~ "0",
		   				  .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope)))) |>
	select(.variable_name, .value, .lower, .upper, .hdi, .rope)

@@

tbl_data |>
	select(-c(.lower, .upper)) |>
	kable(format = "latex",
		  escape = FALSE,
		  col.names = col_names,
		  digits = 3,
		  booktabs = TRUE,
		  align = "lclr",
		  linesep = "") |>
	kable_styling() |>
	add_footnote("$\\beta$: median of the posterior distribution in the probability scale. 95\\% HDI: 95\\% highest density interval of the distribution. $p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
```

```{r timecourse-oxf}
nd <- expand_grid(distinct(data_oxf, condition),
				  timebin_std = timebin_values,
				  age_std = 0)

epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1, 
						  re_formula = NA,
						  ndraws = NULL,
						  value = ".epred")
```

@@

```{r fig-epreds-oxf}
#| label: fig-epreds-oxf
#| fig-cap: "A) Posterior mean predictions of the time course of target fixation in the test phase. Thin lines represent 100 individual posterior predictions. Thick lines indicate the mean of the posterior predictions. B) Posterior mean prediction of the time course of the differences in target looking time between conditions. Thin lines represent 100 individual posterior predictions. Black lines indicate the mean of the posterior predictions."
#| fig-width: 6.5
#| fig-height: 6.5
epreds_summary <- epreds |> 
	ungroup() |> 
	summarise(.value = mean_qi(.epred)[[1]],
			  .lower = mean_qi(.epred)[[2]],
			  .upper = mean_qi(.epred)[[3]],
			  .by = c(condition, timebin_std))

plot_epreds <- epreds |> 
	ggplot(aes(timebin_std, .epred,
			   colour = condition,
			   fill = condition,
			   linetype = condition,
			   shape = condition)) +
	geom_hline(yintercept = 0,
			   colour = "grey") +
	# geom_line(aes(group = interaction(condition, .draw)),
	# 		  alpha = 1/20,
	# 		  linewidth = 3/4,
	# 		  linetype = "solid") +
	stat_summary(fun.data = mean_qi,
				 geom = "ribbon",
				 alpha = 1/4,
				 linewidth = NA) +
	stat_summary(fun = "mean",
				 geom = "line",
				 # colour = "black",
				 linewidth = 3/4) +
	stat_summary(data = data_oxf,
				 aes(y = .elog),
				 fun = "mean",
				 geom = "point",
				 size = 2) +
	labs(x = "Time (ms)",
		 y = "Logit (Target looking)",
		 colour = "Condition",
		 fill = "Condition",
		 linetype = "Condition",
		 shape = "Condition")

epreds_diff <- epreds |> 
	pivot_wider(id_cols = c(timebin_std, .draw),
				names_from = "condition",
				values_from = ".epred",
				names_repair = janitor::make_clean_names) |> 
	mutate(diff_1 = related_non_cognate - unrelated,
		   diff_2 = related_cognate - related_non_cognate) |> 
	pivot_longer(matches("diff"),
				 names_to = "diff",
				 values_to = ".epred",
				 names_prefix = "diff_") |> 
	mutate(diff = factor(diff,
						 levels = c(1, 2),
						 labels = c("Related/Non-cognate - Unrelated",
						 		   "Related/Cognate - Related/Non-cognate")))

plot_diffs <- epreds_diff |> 
	ggplot(aes(timebin_std, .epred)) +
	facet_wrap(~diff) +
	# annotate(geom = "rect",
	# 		 xmin = timebin_values[1],
	# 		 xmax = timebin_values[length(timebin_values)],
	# 		 ymin = rope_interval[1],
	# 		 ymax = rope_interval[2],
	# 		 fill = "red",
	# 		 linewidth = 0,
	# 		 alpha = 1/2,
	# 		 linetype = "dotted") +
	stat_summary(fun.data = mean_qi,
				 geom = "ribbon",
				 fill = "grey",
				 linewidth = NA,
				 alpha = 1/3) +
	stat_summary(aes(group = diff),
				 fun = mean,
				 geom = "line",
				 colour = "black",
				 linewidth = 3/4) +
	geom_hline(yintercept = rope_interval[1],
			   colour = "red",
			   linetype = "dotted") +
	geom_hline(yintercept = rope_interval[2],
			   colour = "red",
			   linetype = "dotted") +
	# geom_line(aes(group = interaction(diff, draw)),
	# 		  alpha = 1/20,
	# 		  linewidth = 3/4,
	# 		  colour = "grey",
	# 		  linetype = "solid") +

	labs(x = "Time (ms)",
		 y = "Logit P(Target looking)",
		 colour = "Comparison",
		 fill = "Comparison",
		 linetype = "Comparison")

>>>>

```{r setup}
#| label: setup
#| echo: false
#| message: false
#| warning: false
# load objects
targets::tar_config_set(
    store = here::here("_targets"),
    script = here::here("_targets.R")
)

@@

targets::tar_load(
    c(
        participants,
        stimuli,
        vocabulary,
        attrition_trials,
        attrition_participants,
        bvq_data,
        gaze,
        data_bcn,
        data_oxf
    )
)

targets::tar_load(
    c(
        model_fits_bcn,
        model_loos_bcn,
        model_fits_oxf,
        model_loos_oxf
    )
)

# prepare data
attrition <- lst(
    participants,
    attrition_participants,
    attrition_trials
) |>
    reduce(inner_join, by = join_by(session_id)) |>
    unnest_wider(matches("all"), names_sep = "_") |>
    rename_with(\(x) gsub("is_valid_gaze_all_|is_valid_vocab_all", "", x))

@@

# set ggplot theme and colour palette
my_theme <- theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_line(colour = "black"),
        text = element_text(size = 12, colour = "black"),
        axis.text = element_text(colour = "black")
    )

@@

options(
    ggplot2.ordinal.fill = clrs[c(1, 4, 5)],
    ggplot2.ordinal.colour = clrs[c(1, 4, 5)],
    ggplot2.discrete.fill = clrs[c(1, 4, 5)],
    ggplot2.discrete.colour = clrs[c(1, 4, 5)],
    ggplot2.continuous.fill = ggplot2::scale_color_gradient,
    ggplot2.continuous.colour = ggplot2::scale_color_gradient
)

@@

```{r}
#| label: participants-numbers-oxf
participants_oxf <- filter(participants, location == "Oxford")

@@

ages <- participants_oxf |>
    summarise(
        n = n(),
        n_participants = n_distinct(child_id),
        across(age, lst(mean, sd, min, max)),
        across(matches("doe_"), lst(mean, sd)),
        age_vctr = list(age),
        .by = c(lp, test_language)
    )

suppressWarnings({
    time_diffs <- participants_oxf |>
        arrange(child_id, session_id, age) |>
        mutate(n_session = 1:n()) |>
        select(child_id, session_id, session_n, age) |>
        filter(child_id %in% participants_oxf$child_id[duplicated(participants_oxf$child_id)]) |>
        pivot_wider(
            id_cols = child_id,
            names_from = session_n,
            values_from = age,
            names_repair = janitor::make_clean_names
        ) |>
        rowwise() |>
        mutate(diff_min = x2 - x1) |>
        ungroup() |>
        summarise(diff_min = min(diff_min, na.rm = TRUE))
})

@@

```{r vocab-values-oxf}
vocabulary_oxf <- inner_join(vocabulary,
    select(participants_oxf, session_id),
    by = join_by(session_id)
)
```

@@

```{r fig-vocabulary-oxf}
#| label: fig-vocabulary-oxf
#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores from the recurrent participants are shown linked."
#| fig-width: 4
#| fig-height: 2.5
vocabulary_oxf |>
    inner_join(filter(attrition_participants, is_valid_participant),
        by = join_by(session_id)
    ) |>
    inner_join(select(participants, child_id, session_id, age_group),
        by = join_by(child_id, session_id)
    ) |>
    ggplot(aes(age_group, l1_prop)) +
    geom_line(aes(group = child_id),
        colour = "grey",
        alpha = 1 / 4, linewidth = 3 / 4
    ) +
    geom_dots(
        dotsize = 2,
        colour = clrs[5],
        fill = clrs[5],
        scale = 1,
        side = "both",
        alpha = 3 / 4
    ) +
    stat_summary(
        fun.data = mean_se,
        geom = "errorbar",
        linewidth = 1 / 2,
        width = 0.1,
        colour = "black",
        show.legend = FALSE
    ) +
    stat_summary(
        fun = mean,
        geom = "point",
        size = 1.5,
        colour = "black",
        show.legend = FALSE
    ) +
    # geom_point(alpha = 1) +
    labs(
        x = "Age (months)",
        y = "Vocabulary size",
        colour = "Group",
        fill = "Group"
    ) +
    scale_y_continuous(
        labels = scales::percent,
        limits = c(0, 1)
    ) +
    theme(
        panel.grid.major.y = element_line(
            linetype = "dotted",
            colour = "grey"
        ),
        legend.position = "top",
        legend.title = element_blank()
    )
```

```{r tbl-participants}
#| label: tbl-participants
#| tbl-cap: "Demographic and linguistic profile of testing sessions."
participants_bcn |>
    unnest_wider(doe) |>
    select(-matches("others")) |>
    arrange(lp, test_language) |>
    distinct(session_id, child_id, .keep_all = TRUE) |>
    summarise(
        n = n(),
        n_participants = length(unique(child_id)),
        across(age, lst(mean, sd, min, max)),
        across(matches("doe_"), lst(mean, sd)),
        # age_vctr = list(age),
        .by = c(lp, test_language)
    ) |>
    gt(
        rowname_col = "test_language",
        groupname_col = "lp"
    ) |>
    summary_rows(
        groups = c("Monolingual", "Bilingual"),
        columns = matches("age"),
        fns = list(Total ~ mean(.)),
        fmt = ~ fmt_number(., decimals = 1, use_seps = FALSE)
    ) |>
    summary_rows(
        groups = c("Monolingual", "Bilingual"),
        columns = c(n, n_participants),
        fns = list(Total ~ sum(.)),
        fmt = ~ fmt_integer(.)
    ) |>
    summary_rows(
        groups = c("Monolingual", "Bilingual"),
        columns = matches("doe"),
        fns = list(Total ~ mean(.)),
        fmt = ~ fmt_number(., decimals = 1, scale_by = 100)
    ) |>
    grand_summary_rows(
        columns = matches("age"),
        fns = list(Total ~ mean(.)),
        fmt = ~ fmt_number(., decimals = 1)
    ) |>
    grand_summary_rows(
        columns = matches("doe"),
        fns = list(Total ~ mean(.)),
        fmt = ~ fmt_number(., decimals = 1, scale_by = 100)
    ) |>
    grand_summary_rows(
        columns = c(n, n_participants),
        fns = list(Total ~ sum(.)),
        fmt = ~ fmt_integer(.)
    ) |>
    # gt_plt_dist(age_vctr, type = "histogram") |>
    fmt_number(is.numeric, decimals = 1) |>
    fmt_integer(c(n, n_participants)) |>
    fmt_number(matches("doe"), decimals = 1, scale_by = 100) |>
    cols_merge(c(age_min, age_max),
        pattern = "{1}-{2}"
    ) |>
    cols_merge(c(age_mean, age_sd),
        pattern = "{1} ({2})"
    ) |>
    cols_merge(c(doe_catalan_mean, doe_catalan_sd),
        pattern = "{1} ({2})"
    ) |>
    cols_merge(c(doe_english_mean, doe_english_sd),
        pattern = "{1} ({2})"
    ) |>
    cols_merge(c(doe_spanish_mean, doe_spanish_sd),
        pattern = "{1} ({2})"
    ) |>
    tab_spanner("Age (months)", matches("age")) |>
    tab_spanner("Catalan", matches("catalan")) |>
    tab_spanner("English", matches("english")) |>
    tab_spanner("Spanish", matches("spanish")) |>
    tab_spanner("Degree of Exposure (%)", matches("doe")) |>
    cols_label(
        n = "Sessions",
        n_participants = "Participants",
        age_mean = "M (SD)",
        age_min = "Range",
        doe_catalan_mean = "M (SD)",
        doe_english_mean = "M (SD)",
        doe_spanish_mean = "M (SD)"
    ) |>
    tab_style(
        cell_text(style = "italic"),
        cells_column_labels()
    ) |>
    tab_style(
        cell_text(style = "italic"),
        cells_column_spanners()
    )
```

```{r vocab-values}
vocabulary_bcn <- vocabulary |>
    inner_join(select(participants_bcn, session_id, lp, age_group),
        by = join_by(session_id)
    )

vocab_means <- vocabulary_bcn |>
    summarise(across(c(total_prop, l1_prop), lst(mean, sd)),
        n = n(),
        .by = c(age_group, lp)
    ) %>%
    mutate(across(matches("prop"), scales::percent)) %>%
    split(paste0("age_", gsub(" months", "", .$age_group))) |>
    map(\(x) split(x, tolower(x$lp)))

n_imputed <- table(vocabulary_bcn$is_imputed)[2]
prop_imputed <- scales::percent(n_imputed / nrow(vocabulary_bcn))
n_pool <- nrow(bvq_data$vocabulary)
```

@@

```{r fig-vocabulary}
#| label: fig-vocabulary
#| fig-cap: "Participant receptive vocabulary sizes across ages and language profiles. Vocabulary size scores are presented using two measures: L1 vocabulary size (proportion of words marked as *Understands* in the vocabulary checklist of the dominant language), and total vocabulary size (proportion of words marked as *Understands* in vocabulary checklists of both dominant and non-dominant languages). Grey lines connect vocabulary size scores from the recurrent participants. For visualisation purposes, participants were group into categorical age groups at 21, 25, 30 months, the ages around which most participants were tested. Only participants included in the final data set are shown."
#| fig-width: 6
#| fig-height: 3.5
vocabulary_bcn |>
    inner_join(filter(attrition_participants, is_valid_participant),
        by = join_by(session_id)
    ) |>
    pivot_longer(c(total_prop, l1_prop),
        names_to = "measure",
        values_to = "prop",
        names_transform = \(x) gsub("_prop", "", x)
    ) |>
    mutate(
        measure = if_else(measure == "l1",
            "L1 vocabulary",
            "Total vocabulary"
        ),
        is_imputed = if_else(is_imputed, "Imputed", "Observed") |>
            factor(levels = c("Observed", "Imputed"))
    ) |>
    ggplot(aes(age_group, prop,
        colour = lp,
        fill = lp
    )) +
    facet_wrap(~measure) +
    geom_line(aes(group = child_id),
        colour = "grey",
        alpha = 1 / 4, linewidth = 3 / 4
    ) +
    geom_dots(aes(side = if_else(lp == "Monolingual", "left", "right")),
        dotsize = 2,
        stroke = 1 / 2,
        scale = 0.5,
        alpha = 3 / 4
    ) +
    stat_summary(
        fun.data = mean_se,
        geom = "errorbar",
        linewidth = 1 / 2,
        width = 0.15,
        colour = "black",
        show.legend = FALSE,
        position = position_dodge(width = 1.15)
    ) +
    stat_summary(
        fun = mean,
        geom = "point",
        size = 1.5,
        colour = "black",
        show.legend = FALSE,
        position = position_dodge(width = 1.15)
    ) +
    # geom_point(alpha = 1) +
    labs(
        x = "Age (months)",
        y = "Vocabulary size",
        colour = "Group",
        fill = "Group"
    ) +
    scale_y_continuous(
        labels = scales::percent,
        limits = c(0, 1)
    ) +
    theme(
        panel.grid.major.y = element_line(
            linetype = "dotted",
            colour = "grey"
        ),
        legend.position = "top",
        legend.title = element_blank()
    )
```

@@

```{r dataset_oxf}
attrition_oxf <- filter(attrition, location == "Oxford")
n_trials <- nrow(attrition_oxf)
n_sessions <- n_distinct(attrition_oxf$session_id)
n_participants <- n_distinct(attrition_oxf$child_id)
n_trials_valid <- nrow(filter(
    attrition_oxf,
    is_valid_participant,
    is_valid_trial
))
n_sessions_valid <- attrition_oxf |>
    distinct(child_id, .keep_all = TRUE) |>
    pull(is_valid_participant) |>
    sum()

n_participants_valid <- n_distinct(
    attrition_oxf[attrition_oxf$is_valid_participant, ]$child_id
)

@@

n_longitudinal <- attrition_oxf |>
    filter(
        is_valid_participant,
        is_valid_trial
    ) |>
    distinct(child_id, session_n) |>
    count(child_id, name = "times") |>
    count(times)

@@

```{r coefs-oxf}
var_labels <- c(
    "b_Intercept" = "Intercept",
    "b_age_std" = "Age (+1 SD)",
    "b_condition1" = "Condition (U vs. RN)",
    "b_condition2" = "Condition (RN vs. RC)"
)

model_summary <- get_posterior_summary(model_fits_oxf$fit_oxf_1,
    data_bcn,
    vars_dict = var_labels,
    rope_interval = rope_interval
)

coefs <- model_summary |>
    mutate(
        .value = sprintf("%.3f", .value),
        .ci = sprintf("[%.3f, %.3f]", .lower, .upper),
        .rope = scales::percent(.rope, accuracy = 0.01)
    ) |>
    split(janitor::make_clean_names(model_summary$.variable))
```

@@

tbl_data <- model_summary |>
    select(.variable_name, .value, .lower, .upper, .rope, .type) |>
    mutate(
        .variable_name = gsub("×", "$\\\\times$", .variable_name),
        .hdi = sprintf("[%.3f, %.3f]", .lower, .upper),
        .rope = case_when(is.na(.rope) ~ "-",
            .rope > 0.9999 ~ "1",
            .rope < 0.00001 ~ "0",
            .default = sub("^(-?)0.", "\\1.", sprintf("%.3f", .rope))
        )
    ) |>
    select(.variable_name, .value, .lower, .upper, .hdi, .rope)

@@

tbl_data |>
    select(-c(.lower, .upper)) |>
    kable(
        format = "latex",
        escape = FALSE,
        col.names = col_names,
        digits = 3,
        booktabs = TRUE,
        align = "lclr",
        linesep = ""
    ) |>
    kable_styling() |>
    add_footnote("$\\beta$: median of the posterior distribution in the probability scale. 95\\% HDI: 95\\% highest density interval of the distribution. $p(\\text{ROPE})$: overlap between the 95\\% HDI and the ROPE, indicating the posterior probability that the true value of the coefficient is equivalent to zero.", notation = "none", escape = FALSE)
```

```{r timecourse-oxf}
nd <- expand_grid(distinct(data_oxf, condition),
    timebin_std = timebin_values,
    age_std = 0
)

epreds <- add_epred_draws(nd, model_fits_oxf$fit_oxf_1,
    re_formula = NA,
    ndraws = NULL,
    value = ".epred"
)
```

@@

```{r fig-epreds-oxf}
#| label: fig-epreds-oxf
#| fig-cap: "A) Posterior mean predictions of the time course of target fixation in the test phase. Thin lines represent 100 individual posterior predictions. Thick lines indicate the mean of the posterior predictions. B) Posterior mean prediction of the time course of the differences in target looking time between conditions. Thin lines represent 100 individual posterior predictions. Black lines indicate the mean of the posterior predictions."
#| fig-width: 6.5
#| fig-height: 6.5
epreds_summary <- epreds |>
    ungroup() |>
    summarise(
        .value = mean_qi(.epred)[[1]],
        .lower = mean_qi(.epred)[[2]],
        .upper = mean_qi(.epred)[[3]],
        .by = c(condition, timebin_std)
    )

plot_epreds <- epreds |>
    ggplot(aes(timebin_std, .epred,
        colour = condition,
        fill = condition,
        linetype = condition,
        shape = condition
    )) +
    geom_hline(
        yintercept = 0,
        colour = "grey"
    ) +
    # geom_line(aes(group = interaction(condition, .draw)),
    # 		  alpha = 1/20,
    # 		  linewidth = 3/4,
    # 		  linetype = "solid") +
    stat_summary(
        fun.data = mean_qi,
        geom = "ribbon",
        alpha = 1 / 4,
        linewidth = NA
    ) +
    stat_summary(
        fun = "mean",
        geom = "line",
        # colour = "black",
        linewidth = 3 / 4
    ) +
    stat_summary(
        data = data_oxf,
        aes(y = .elog),
        fun = "mean",
        geom = "point",
        size = 2
    ) +
    labs(
        x = "Time (ms)",
        y = "Logit (Target looking)",
        colour = "Condition",
        fill = "Condition",
        linetype = "Condition",
        shape = "Condition"
    )

epreds_diff <- epreds |>
    pivot_wider(
        id_cols = c(timebin_std, .draw),
        names_from = "condition",
        values_from = ".epred",
        names_repair = janitor::make_clean_names
    ) |>
    mutate(
        diff_1 = related_non_cognate - unrelated,
        diff_2 = related_cognate - related_non_cognate
    ) |>
    pivot_longer(matches("diff"),
        names_to = "diff",
        values_to = ".epred",
        names_prefix = "diff_"
    ) |>
    mutate(diff = factor(diff,
        levels = c(1, 2),
        labels = c(
            "Related/Non-cognate - Unrelated",
            "Related/Cognate - Related/Non-cognate"
        )
    ))

plot_diffs <- epreds_diff |>
    ggplot(aes(timebin_std, .epred)) +
    facet_wrap(~diff) +
    # annotate(geom = "rect",
    # 		 xmin = timebin_values[1],
    # 		 xmax = timebin_values[length(timebin_values)],
    # 		 ymin = rope_interval[1],
    # 		 ymax = rope_interval[2],
    # 		 fill = "red",
    # 		 linewidth = 0,
    # 		 alpha = 1/2,
    # 		 linetype = "dotted") +
    stat_summary(
        fun.data = mean_qi,
        geom = "ribbon",
        fill = "grey",
        linewidth = NA,
        alpha = 1 / 3
    ) +
    stat_summary(aes(group = diff),
        fun = mean,
        geom = "line",
        colour = "black",
        linewidth = 3 / 4
    ) +
    geom_hline(
        yintercept = rope_interval[1],
        colour = "red",
        linetype = "dotted"
    ) +
    geom_hline(
        yintercept = rope_interval[2],
        colour = "red",
        linetype = "dotted"
    ) +
    # geom_line(aes(group = interaction(diff, draw)),
    # 		  alpha = 1/20,
    # 		  linewidth = 3/4,
    # 		  colour = "grey",
    # 		  linetype = "solid") +

    labs(
        x = "Time (ms)",
        y = "Logit P(Target looking)",
        colour = "Comparison",
        fill = "Comparison",
        linetype = "Comparison"
    )

plot_epreds + plot_diffs +
    plot_layout(ncol = 1) &
    plot_annotation(tag_levels = "A") &
    # scale_y_continuous(limits = c(0.25, 0.75)) +
    scale_x_continuous(
        breaks = make_std(
            seq(0, 17, 3),
            mean(data_bcn$timebin),
            sd(data_bcn$timebin)
        ),
        labels = \(x) format(seq(3e2, 2e3, 3e2),
            big.mark = ","
        )
    ) &
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        panel.grid.major.y = element_line(
            colour = "grey",
            linetype = "dotted"
        )
    )
```
